Extracting data for time slice analyses

### 2017-11-28 analyses/01-extract-data-for-analyses.Rmd
Change .tre to .nex for Brusatte data

## The latest version of dispRity 
install_github("TGuillerme/dispRity", ref = "release")
library(dispRity) 
```

@@

And that's it... we now have all the processed data for running the `dispRity` package properly: the distance matrices(that we will use to build the `morphospace`), and the cleaned tree (`tree`). Remember that for the `time.subsamples` function, you can use the `inc.nodes` logical option to include nodes or not!

>>>>

## The latest version of dispRity 
install_github("TGuillerme/dispRity")
library(dispRity) 
```

@@

And that's it... we now have all the processed data for running the `dispRity` package properly: the distance matrices(that we will use to build the `morphospace`), and the cleaned tree (`tree`). Remember that for the `time.subsets` function, you can use the `inc.nodes` logical option to include nodes or not!
